Is Archaeology a science? Insights and imperatives from 10,000 articles and a year of reproducibility reviews

### 2025-05-30 analysis/paper/paper.qmd
update with edits from JAS editor

To objectively quantify the diversity of modern archaeological practice across a scale of relative hardness or softness, as an evaluation of its status as a science, and the place of this journal in context of other archaeology journals, I take a bibliometric approach. This approach is based on @fanelliBibliometricEvidenceHierarchy2013, who examined the hardness and softness of 12 disciplines using scholarly publication parameters. @fanelliBibliometricEvidenceHierarchy2013 found a spectrum of statistically significant variation in bibliometric variables from the physical to the social sciences, with papers tending at the softer end of the spectrum tending to have fewer co-authors, use less substantive titles, have longer texts, cite older literature, and have a higher diversity of sources. In @fanelliBibliometricEvidenceHierarchy2013's analysis harder sciences include Space Science, Physics, Chemistry, softer sciences include social sciences (Psychiatry, Psychology, Economics, Business, and General Social Sciences), and the Humanities define the soft end of the spectrum. Following @fanelliBibliometricEvidenceHierarchy2013, I quantify the number of authors, length of article, relative title length, age of references, and diversity of references for a large sample of peer-reviewed journal articles.

These parameters are useful because of how they signify consensus in a research community. A larger number of authors on a paper reflects collaboration of people working together on a common goal. Collaborators have specialized roles, each of whom has the ability to study a part of the problem with high accuracy and detail, with harder fields having larger groups of collaborators [@zuckerman1972age]. Reflecting this collaboration group size, harder disciplines tend to have higher average numbers of authors on papers. Article length has an inverse correlation with field hardness. In low-consensus, or softer, fields, papers must be longer to present justification, nuance and contextualization of results. While article length is constrained by journal requirements, leaving individual authors with little freedom to vary, journal requirements are typically set by editors who are professional archaeologists keen to tailor their journal to be attractive and relevant other members of the discipline. Thus journal requirements for article length will reflect the norms and of the discipline at any given time. The number of substantive and informative words in an article's title tends to be positively correlated with article length in harder disciplines [@yitzhakiRelationTitleLength2002; @yitzhakiVariationInformativityTitles1997], reflecting a focus on empiricism and efficiency that is characteristic of high-consensus disciplines. While @yitzhakiRelationTitleLength2002 removed stop-words (e.g. prepositions, articles, conjunctions, etc.) to calculate article length, in order to generate results for comparison with @fanelliBibliometricEvidenceHierarchy2013 I follow his method of dividing the total word count of the article title by the total number of pages of the article to compute relative title length.

@@

The entire R code [@rcoreteamLanguageEnvironmentStatistical2024] used for all the analysis and visualizations contained in this paper is included in the Supplementary Online Materials at https://doi.org/10.5281/zenodo.14897253 to enable re-use of materials and improve reproducibility and transparency [@marwickComputationalReproducibilityArchaeological2017]. All the figures, tables, and statistical test results presented here can be independently reproduced with the code and data in this compendium [@doi:10.1080/00031305.2017.1375986]. The R code is released under the MIT license, the data as CC-0, and figures as CC-BY, to enable maximum re-use.

@@

@fig-compare-other-fields shows the distribution of bibliometric variables for archaeology in context of data from other fields presented by @fanelliBibliometricEvidenceHierarchy2013. The most striking indicator of archaeology as a hard science is the number of authors, where it is between the social sciences and physics. Archaeology is a close fit with the social sciences in relative title length. It is between the social sciences and humanities in recency of references and diversity of references. The clearest indicator of archaeology as a soft science is article length where it is similar to the humanities. Overall, archaeology does not sit squarely at either end of the hard-soft spectrum. It is generally not a harder science than the social sciences, with the exception of collaborator group sizes.

@@

The *Journal of Cultural Heritage* is the only journal that consistently ranks as hard across all variables, occurring in the top five journals for all five metrics. This journal primarily publishes materials science and computational analyses related to conservation and preservation of historic objects in museums and other collections. Authors of papers in recent issues have affiliations with museums, cultural heritage programs, and chemistry, engineering, and physics departments at European and Chinese universities. Notably, papers in this journal typically do not engage in questions or debates about past human behaviour or culture. The absence of these questions in research published in this journal makes it an outlier here, since these questions are central to a common definition of archaeology as 'cultural anthropology of the past', a phrase first found in @leroigourhan1946 and repeated in widely-used contemporary undergraduate textbooks such as @renfrew2024. Most archaeologists would likely be surprised at the decision by Clarivate to include the *Journal of Cultural Heritage* in their category of archaeology journals, leading to this result in @fig-variation-by-journal where the hardest archaeology journal publishes papers that are not very archaeological at all because they do not engage with anthropological topics.

@@

The PCA results in @fig-pca shows that PC1 captures most of the variance in the metrics (`r variance_explained[1]`%) and is reasonable proxy for the hard-soft spectrum, with *Journal of Cultural Heritage* representing the hard extreme on the right and *Journal of Archaeological Research* representing the soft extreme on the left. The variables that contribute to variation in PC1 are title length, number of pages, and the diversity of references. Journals with higher PC1 values have articles with longer titles, fewer pages, and less diverse reference lists. The distribution of PC1 values is skewed left, with most of the journals concentrated at the harder end of the spectrum. Variation in PC2 is influenced by the number of authors and recency of references. The distribution of PC2 values reveals additional structure to the data and can be roughly separated into generalist journals in the negative range of the PC2 axis (e.g. *American Antiquity*, *Antiquity*, *Advances in Archaeological Practice*), characterised by fewer authors and more recent references. In the positive range of the PC2 axis are more specialised journals, characterised by higher numbers of authors and less recent references cited (e.g. *Environmental Archaeology*, *Geoarchaeology*, *Archaeological Research in Asia*, *Journal of Island and Coastal Archaeology*). The *Journal of Archaeological Science* sits about midway between these two groups, reflecting its relevance to both specialised and generalist communities of practice in archaeology.

@@

This macroscopic perspective derived from an analysis of the ways thousands of archaeologists communicate their research has produced a complex picture of archaeology as a science. In the context of a broad spectrum of other research areas, archaeologists behave like social scientists. We are harder than typical social scientists in tending to form larger groups of collaborators more often, and softer in sometimes writing longer articles than more resemble humanities scholarship. The outlook for the future of archaeology is also complex, with three out of five of the bibliometric variables trending towards more humanistic styles of working, but the discipline showing more extreme values in some metrics towards both hard and soft sciences after about 2010. Among archaeology journals, we see distinct communities of practice reflected in the PCA results that are very close together on the hard-soft spectrum, but have minor differences in their communication styles, perhaps due to cultural differences in writing traditions inherited from parent disciplines such as geology and biology [@becher2001academic].

While these bibliometric variables provide several interesting insights into the status of archaeology as a science, via measurement of consensus, and are important for moving the debate beyond discussions of a small number of case studies, they miss a crucial factor that separates scientific practice from non-science. This is reproducibility, which, according to a report for the US National Science Foundation [@cacioppo2015social], "refers to the ability of a researcher to duplicate the results of a prior study using the same materials as were used by the original investigator. That is, a second researcher might use the same raw data to build the same analysis files and implement the same statistical analysis in an attempt to yield the same results... Reproducibility is a minimum necessary condition for a finding to be believable and informative." Scientific reproducibility is a factor contributing to the hardness of a field. Specifically, reproducibility is linked to to concept of consensus in a field because if more researchers provide sufficient detail for others to reproduce their results, then consensus on new knowledge can more often, and more, rapidly be established. The importance of this factor can be traced to Irish chemist Robert Boyle (1627-1691), best known for his experiments with vacuum pumps [@shapin2011leviathan]. Boyle was concerned about the secrecy common among experimentalists in the 17th century and aimed to shift the culture from valuing direct in-person witnessing of scientific demonstrations towards meticulous written communications that were detailed enough to enable a reader to successfully undertake the experiment themselves, independent of the original author.

@@

At the time of writing (January 2025) we have completed 47 reproducibility reviews of 25 manuscripts submitted to JAS (most papers required multiple reviews). Of these, 11 have been published in JAS to date. Seven of these eleven papers fully passed the reproducibility review, resulting in a success rate, by one measure, of 63%. Four of the seven papers could be fully reproduced on my first attempt, the others required additional input from the authors. For comparison with reproducibility studies in other fields reported above, the seven fully reproducible papers should be divided by the 25 reviewed for reproducibility, resulting in a 28% success rate. Expanding the denominator to include the total number of research articles published in JAS from May 2024 (when the first article to pass the reproducibility review, @herskindComputationalLinguisticMethodology2024, was published) to January 2025 (n = 97) offers another perspective. These 97 articles that could have been eligible for reproducibility review had the authors used an open source programming language (e.g. instead of commercial software such as Microsoft Excel or SPSS, etc.). Under this broader scope, the success rate is 7%, a result also found in a study of 497 papers in 9 ecology journals [@kellnerFunctionalCodeRare2025]. In any case, the computational reproducibility of archaeological research is generally on the low end of the distribution of values available from a variety of hard and soft sciences.

@@

Panels D and E of @fig-aer-summary summarise the common issues that resulted in irreproducible results. The most common issue was an incomplete compendium. This ranges from missing data files down to missing lines of code. In most cases this can attributed to accidental carelessness, with the exception of two cases where data was unavailable due to licensing restrictions. Unspecified or under-specified dependencies is another common issue that prevents code from running. This refers to the software packages in addition to R or Python that an author used to do specialized analyses and visualisations, (e.g. dplyr for R or numpy for Python). If an author does not clearly specify the name and version number of the packages that they used for their analysis, it can be very time-consuming or impossible to correctly identify these because many packages have functions with similar names, and functions in any one package can change they way they behave as the developers update their package. Other reasons why papers failed the reproducibility review is that the paths to data files were incorrectly specified (likely a result of the author reorganising their compendium after completing their analysis, or omitting data files from the materials submitted for review), and errors returned by functions, which have diverse causes.

@@

Second, authors should include in their compendium a README document that describes to readers the folders and files contained in the project [@abdillHowtoGuideCode2024]. The README file is typically the first file that a reader will look at in a compendium so it should include brief instructions to guide the user to a successful reproduction of the original results (e.g. what order to run the code files in). A README should also briefly describe the contents of the compendium, where other necessary files can be obtained (e.g. data files that cannot be included in the compendium due for ethical or other reasons), the key software packages needed and the version numbers that the authors used, and if the analysis takes more than a few minutes to run on a typical laptop, the hardware resources and compute time used by the author.

@@

The simplest way for archaeologists to improve here is to write the names and version numbers of the software and packages they used in their README file, as we see in @herskindComputationalLinguisticMethodology2024 and @monnaStudyingSerialityMaterial2024. For more complex research projects, i.e. those using five or more packages or machine learning algorithms, authors should use dependency management tools to keep track of the packages and version numbers needed to reproduce their results. This is an active area of development, and while there are many tools currently available, the most robust and widely used include renv for R [@renv, see examples in @vernonMethodDefiningDispersed2024 and @ragnoSheepGoatsTaxonomic2024] and conda and poetry for Python [@conda2023; @poetry2023].

A more comprehensive solution, and the leading best practice for managing dependencies in many computationally intensive fields using Python in particular, is to include a Dockerfile in the compendium [@moreauContainersComputationalReproducibility2023]. This is a set of machine- and human-readable instructions that enables a user to recreate the author's computational environment (including those requirements beyond the R or Python packages) on another computer [@nustTenSimpleRules2020]. Dockerfiles are gradually being adopted by archaeologists, see @cremaModellingDiffusionInnovation2024 and @liaoApplyingMaskRCNN2024 for examples, and most of our reproducibility reviews include a recommendation that the author include a Dockerfile to manage complex dependencies efficiently.

Finally, for analyses that are not highly time-consuming (which was over 90% of the sample), authors should re-run their code more than once, and ideally not on the same computer (e.g. by another co-author of the paper), before submission to confirm everything works as expected [@abdillHowtoGuideCode2024; @rothTenPrinciplesReliable2025]. This ensures portability and likely also prevents issues relating to path and function errors. Complex and time-consuming analyses should use pipeline or workflow management tools, e.g. GNU Make, Luigi, Snakemake, or Targets, to document the relationship of the files and folders in a machine-readable format and simplify running and re-running code by others [@wrattenReproducibleScalableShareable2021; @landau2021targets].

@@

```{r}
#| label: fig-checklist
#| fig-cap: "Checklist summarising a small set of some of the simplest tasks authors can do that have high potential to increase reproducibility"
#| fig-height: 4

>>>>

To objectively quantify the diversity of modern archaeological practice across a scale of relative hardness or softness, as an evaluation of its status as a science, and the place of this journal in context of other archaeology journals, I take a bibliometric approach. This approach is based on @fanelliBibliometricEvidenceHierarchy2013, who examined the hardness and softness of 12 disciplines using scholarly publication parameters. @fanelliBibliometricEvidenceHierarchy2013 found a spectrum of statistically significant variation in bibliometric variables from the physical to the social sciences, with papers at the softer end of the spectrum tending to have fewer co-authors, use less substantive titles, have longer texts, cite older literature, and have a higher diversity of sources. In Fanelli and Glänzel's [-@fanelliBibliometricEvidenceHierarchy2013] analysis harder sciences include Space Science, Physics, Chemistry, softer sciences include social sciences (Psychiatry, Psychology, Economics, Business, and General Social Sciences), and the Humanities define the soft end of the spectrum. Following @fanelliBibliometricEvidenceHierarchy2013, I quantify the number of authors, length of article, relative title length, age of references, and diversity of references for a large sample of peer-reviewed journal articles.

These parameters are useful because of how they signify consensus in a research community. A larger number of authors on a paper reflects collaboration of people working together on a common goal. Collaborators have specialized roles, each of whom has the ability to study a part of the problem with high accuracy and detail, with harder fields having larger groups of collaborators [@zuckerman1972age]. Reflecting this collaboration group size, harder disciplines tend to have higher average numbers of authors on papers. Article length has an inverse correlation with field hardness. In low-consensus, or softer, fields, papers must be longer to present justification, nuance and contextualization of results. While article length is constrained by journal requirements, leaving individual authors with little freedom to vary, journal requirements are typically set by editors who are professional archaeologists keen to tailor their journal to be attractive and relevant to other members of the discipline. Thus journal requirements for article length will reflect the norms of the discipline at any given time. The number of substantive and informative words in an article's title tends to be positively correlated with article length in harder disciplines [@yitzhakiRelationTitleLength2002; @yitzhakiVariationInformativityTitles1997], reflecting a focus on empiricism and efficiency that is characteristic of high-consensus disciplines. While @yitzhakiRelationTitleLength2002 removed stop-words (e.g. prepositions, articles, conjunctions, etc.) to calculate article length, in order to generate results for comparison with @fanelliBibliometricEvidenceHierarchy2013 I follow their method of dividing the total word count of the article title by the total number of pages of the article to compute relative title length.

@@

The entire R code [@rcoreteamLanguageEnvironmentStatistical2024] used for all the analysis and visualizations contained in this paper is at https://doi.org/10.5281/zenodo.14897253 to enable re-use of materials and improve reproducibility and transparency [@marwickComputationalReproducibilityArchaeological2017]. All the figures, tables, and statistical test results presented here can be independently reproduced with the code and data in this compendium [@doi:10.1080/00031305.2017.1375986]. The R code is released under the MIT license, the data as CC-0, and figures as CC-BY, to enable maximum re-use.

@@

@fig-compare-other-fields shows the distribution of bibliometric variables for archaeology in the context of data from other fields presented by @fanelliBibliometricEvidenceHierarchy2013. The most striking indicator of archaeology as a hard science is the number of authors, where it is between the social sciences and physics. Archaeology is a close fit with the social sciences in relative title length. It is between the social sciences and humanities in recency of references and diversity of references. The clearest indicator of archaeology as a soft science is article length where it is similar to the humanities. Overall, archaeology does not sit squarely at either end of the hard-soft spectrum. It is generally not a harder science than the social sciences, with the exception of collaborator group sizes.

@@

The *Journal of Cultural Heritage* is the only journal that consistently ranks as hard across all variables, occurring in the top five journals for all five metrics. This journal primarily publishes materials science and computational analyses related to conservation and preservation of historic objects in museums and other collections. Authors of papers in recent issues have affiliations with museums, cultural heritage programs, and chemistry, engineering, and physics departments at European and Chinese universities. Notably, papers in this journal typically do not engage in questions or debates about past human behaviour or culture. The absence of these questions in research published in this journal makes it an outlier here, since these questions are central to a common definition of archaeology as 'cultural anthropology of the past', a phrase first found in @leroigourhan1946 and repeated in widely-used contemporary undergraduate textbooks such as @renfrew2024. Most archaeologists would likely be surprised at the decision by Clarivate to include the *Journal of Cultural Heritage* in their category of archaeology journals, leading to this result in @fig-variation-by-journal where the hardest archaeology journal publishes papers that are not very archaeological because they do not engage with anthropological topics.

@@

The PCA results in @fig-pca shows that PC1 captures most of the variance in the metrics (`r variance_explained[1]`%) and is a reasonable proxy for the hard-soft spectrum, with *Journal of Cultural Heritage* representing the hard extreme on the right and *Journal of Archaeological Research* representing the soft extreme on the left. The variables that contribute to variation in PC1 are title length, number of pages, and the diversity of references. Journals with higher PC1 values have articles with longer titles, fewer pages, and less diverse reference lists. The distribution of PC1 values is skewed left, with most of the journals concentrated at the harder end of the spectrum. Variation in PC2 is influenced by the number of authors and recency of references. The distribution of PC2 values reveals additional structure to the data and can be roughly separated into generalist journals in the negative range of the PC2 axis (e.g. *American Antiquity*, *Antiquity*, *Advances in Archaeological Practice*), characterised by fewer authors and more recent references. In the positive range of the PC2 axis are more specialised journals, characterised by higher numbers of authors and less recent references cited (e.g. *Environmental Archaeology*, *Geoarchaeology*, *Archaeological Research in Asia*, *Journal of Island and Coastal Archaeology*). The *Journal of Archaeological Science* sits about midway between these two groups, reflecting its relevance to both specialised and generalist communities of practice in archaeology.

@@

This macroscopic perspective derived from an analysis of the ways thousands of archaeologists communicate their research has produced a complex picture of archaeology as a science. In the context of a broad spectrum of other research areas, archaeologists behave like social scientists. We are harder than typical social scientists in tending to form larger groups of collaborators more often, and softer in sometimes writing longer articles that more resemble humanities scholarship. The outlook for the future of archaeology is also complex, with three out of five of the bibliometric variables trending towards more humanistic styles of working, but the discipline showing more extreme values in some metrics towards both hard and soft sciences after about 2010. Among archaeology journals, we see distinct communities of practice reflected in the PCA results that are very close together on the hard-soft spectrum, but have minor differences in their communication styles, perhaps due to cultural differences in writing traditions inherited from parent disciplines such as geology and biology [@becher2001academic].

While these bibliometric variables provide several interesting insights into the status of archaeology as a science, via measurement of consensus, and are important for moving the debate beyond discussions of a small number of case studies, they miss a crucial factor that separates scientific practice from non-science. This is reproducibility, which, according to a report for the US National Science Foundation [@cacioppo2015social], "refers to the ability of a researcher to duplicate the results of a prior study using the same materials as were used by the original investigator. That is, a second researcher might use the same raw data to build the same analysis files and implement the same statistical analysis in an attempt to yield the same results... Reproducibility is a minimum necessary condition for a finding to be believable and informative." Scientific reproducibility is a factor contributing to the hardness of a field. Specifically, reproducibility is linked to concept of consensus in a field because if more researchers provide sufficient detail for others to reproduce their results, then consensus on new knowledge can more often, and more rapidly, be established. The importance of this factor can be traced to Irish chemist Robert Boyle (1627-1691), best known for his experiments with vacuum pumps [@shapin2011leviathan]. Boyle was concerned about the secrecy common among experimentalists in the 17th century and aimed to shift the culture from valuing direct in-person witnessing of scientific demonstrations towards meticulous written communications that were detailed enough to enable a reader to successfully undertake the experiment themselves, independent of the original author.

@@

At the time of writing (January 2025) we have completed 47 reproducibility reviews of 25 manuscripts submitted to JAS (most papers required multiple reviews). Of these, 11 have been published in JAS to date. Seven of these eleven papers fully passed the reproducibility review, resulting in a success rate, by one measure, of 63%. Four of the seven papers could be fully reproduced on my first attempt, the others required additional input from the authors. For comparison with reproducibility studies in other fields reported above, the seven fully reproducible papers should be divided by the 25 reviewed for reproducibility, resulting in a 28% success rate. Expanding the denominator to include the total number of research articles published in JAS from May 2024 (when the first article to pass the reproducibility review, @herskindComputationalLinguisticMethodology2024, was published) to January 2025 (n = 97) offers another perspective. These 97 articles that could have been eligible for reproducibility review had the authors used an open source programming language (e.g. instead of commercial software such as Microsoft Excel or SPSS, etc.). Under this broader scope, the success rate is 7%, a result also found in a study of 497 papers in 9 ecology journals [@kellnerFunctionalCodeRare2025]. By any measure, the computational reproducibility of archaeological research is generally on the low end of the distribution of values available from a variety of hard and soft sciences.

@@

Panels D and E of @fig-aer-summary summarise the common issues that resulted in irreproducible results. The most common issue was an incomplete compendium. This ranges from missing data files down to missing lines of code. In most cases this can be attributed to accidental carelessness, with the exception of two cases where data was unavailable due to licensing restrictions. Unspecified or under-specified dependencies is another common issue that prevents code from running. This refers to the software packages in addition to R or Python that an author used to do specialized analyses and visualisations, (e.g. dplyr for R or numpy for Python). If an author does not clearly specify the name and version number of the packages that they used for their analysis, it can be very time-consuming or impossible to correctly identify these because many packages have functions with similar names, and functions in any one package can change the way they behave as the developers update their package. Other reasons why papers failed the reproducibility review is that the paths to data files were incorrectly specified (likely a result of the author reorganising their compendium after completing their analysis, or omitting data files from the materials submitted for review), and errors returned by functions, which have diverse causes.

@@

Second, authors should include in their compendium a README document that describes to readers the folders and files contained in the project [@abdillHowtoGuideCode2024]. The README file is typically the first file that a reader will look at in a compendium so it should include brief instructions to guide the user to a successful reproduction of the original results (e.g. what order to run the code files in). A README should also briefly describe the contents of the compendium, where other necessary files can be obtained (e.g. data files that cannot be included in the compendium due to ethical or other reasons), the key software packages needed and the version numbers that the authors used, and if the analysis takes more than a few minutes to run on a typical laptop, the hardware resources and compute time used by the author.

@@

The simplest way for archaeologists to improve here is to write the names and version numbers of the software and packages they used in their README file, as we see in @herskindComputationalLinguisticMethodology2024 and @monnaStudyingSerialityMaterial2024. For more complex research projects, i.e. those using five or more packages or machine learning algorithms, authors should use dependency management tools to keep track of the packages and version numbers needed to reproduce their results. This is an active area of development, and while there are many tools currently available, the most robust and widely used include renv for R [@renv], see examples in @vernonMethodDefiningDispersed2024 and @ragnoSheepGoatsTaxonomic2024, and conda and poetry for Python [@conda2023; @poetry2023].

A more comprehensive solution, and the leading best practice for managing dependencies in many computationally intensive fields using Python in particular, is to include a Dockerfile in the compendium [@moreauContainersComputationalReproducibility2023]. This is a set of machine- and human-readable instructions that enables a user to recreate the author's computational environment (including those requirements beyond the R or Python packages) on another computer [@nustTenSimpleRules2020]. Dockerfiles are gradually being adopted by archaeologists, see @cremaModellingDiffusionInnovation2024 and @liaoApplyingMaskRCNN2024 for examples. Most of our reproducibility reviews include a recommendation that the authors include a Dockerfile to manage complex dependencies efficiently.

Finally, for analyses that are not highly time-consuming (which was over 90% of the sample), authors should re-run their code more than once, and ideally not on the same computer (e.g. by another co-author of the paper), before submission to confirm everything works as expected [@abdillHowtoGuideCode2024; @rothTenPrinciplesReliable2025]. This ensures the project is self-contained and portable and will help the authors detect and solve issues relating to path and function errors before they submit their work for review. Complex and time-consuming analyses should use pipeline or workflow management tools, e.g. GNU Make, Luigi, Snakemake, or Targets, to document the relationship of the files and folders in a machine-readable format and simplify running and re-running code by others [@wrattenReproducibleScalableShareable2021; @landau2021targets].

@@

```{r}
#| label: fig-checklist
#| fig-cap: "Checklist summarising a small set of some of the simplest tasks authors can do that have high potential to increase reproducibility. ML = Machine Learning, DL = Deep Learning, MCMC = Monte Carlo Markov Chain simulations"
#| fig-height: 4
